Study of Illumination Dependency in the Dynamic Laser Speckle Analysis

### 2019-08-05 article/article_1.tex
corrigindo pontos a resaltar

In the paper piece test, we considered that no material is completely inert, 
and consequently, 
a dynamic speckle analysis will show us how the speckle light intensity variations can be interpret as the sample activity level or as the set default level noise in the test,
we use the first case,
the effect in the speckle light intensity occasioned by the laser light intensity variation.

>>>>

In the paper piece test, we considered that none material is completely inert and, consequently, 
the observed signal  in the  dynamic speckle analysis has more than noise.
